Thesis Title

### 2022-04-29 chapters/chapter_8.tex

Modern software engineering advocates reliable software testing standards and best practices. Different approaches are employed: from unit testing to system testing \cite{krafczyk_scientific_2019}[2], going from testing every individual component to testing a tool as a whole (Fig. \ref{}). The extent of testing is a balance between the resources available and increasing sustainability and reproducibility. Continuous Integration (CI), where code changes are frequently integrated and assertion of the new code’s correctness before integration is often automatedly performed through tests, provides a robust approach for ensuring the reproducibility of scientific results without requiring human interaction. Comprehensive testing of scientific software might prevent computational errors which subsequently lead to erroneous results and retractions \cite{}[3, 4]. However, the role of testing extends beyond that, as it also provides a way to measure software coverage, and therefore its robustness, allowing for reported issues to be converted into testable actions (regression tests), and the expansion and refactoring of existing code without compromising its function.

>>>>

Modern software engineering advocates reliable software testing standards and best practices. Different approaches are employed: from unit testing to system testing \cite{krafczyk_scientific_2019}[2], going from testing every individual component to testing a tool as a whole (Fig. \ref{}). The extent of testing is a balance between the resources available and increasing sustainability and reproducibility. Continuous Integration (CI), where code changes are frequently integrated and assertion of the new code’s correctness before integration is often automatedly performed through tests, provides a robust approach for ensuring the reproducibility of scientific results without requiring human interaction. Comprehensive testing of scientific software might prevent computational errors which subsequently lead to erroneous results and retractions \cite{chang_retraction_2006,hall_retraction_2007}[3, 4]. However, the role of testing extends beyond that, as it also provides a way to measure software coverage, and therefore its robustness, allowing for reported issues to be converted into testable actions (regression tests), and the expansion and refactoring of existing code without compromising its function.

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{figures/chapter 8/}
\caption{Testing strategies. (a) White-box vs. black-box testing. In white-box testing, the tester knows the underlying code and structure of the software, where the tester does not know this in black-box testing. Note that this distinction is not strictly dichotomous and is considered less useful nowadays (b) Unit vs. integration vs. system testing. When software comprises several modules, it is possible to test each single module (unit testing), groups of related modules (integration testing) or all modules (system testing). Note that the terms white-box testing and unit testing are sometimes used interchangeably but relate to different concepts}
\label{fig:chap4_figure1}
\end{figure*}
